A Unified Treatment of Tractability for Approximation Problems Defined on Hilbert Spaces

### 2023-07-18 GeneralizedTractability2023July17.tex
Updates from Overleaf

For the case $\theUB(d)> 0$, we utilize the upper bound \eqref{eq:compUP_rest}, specializing to the case of $\thed=d$ and $N = \min\left\{\right\}\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right\}$:
\begin{align*}
       \comp(\varepsilon,d)
       & \le T(\varepsilon^{-1},d, \vp) \Biggl [ \frac{\min\left{}\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right\}}{T(\varepsilon^{-1},d, \vp)}  + \underbrace{\sum_{i = \min\left\{\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right\}}^{\theUB(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} + 1/ T(\lambda_{\theUB(d), d}^{-1},d,\vp) \text{ by \eqref{eq:strong_rest_tractiff}} }
        \Biggr] \\
       & \le T(\varepsilon^{-1},d,\vp)\left[\frac{ L_{\vp}\, T(0,d,\vp)+1}{T(0,d, \vp)} + S_{\vp} + \frac{1}{T(\lambda_{\theUB(d), d}^{-1},d,\vp)} \right]
       \qquad \text{by \eqref{eq:Tnondecreasing}}\\
       & \le T(\varepsilon^{-1},d,\vp) \underbrace{\left[L_{\vp} + \frac{2}{T(0,1, \vp)} + S_{\vp} \right]}_{=:C_{\vp}}
       \qquad \text{by \eqref{eq:Tnondecreasing}}\\
       & =  C_{\vp}T(\varepsilon^{-1},d,\vp).
\end{align*}
This means that we have strong $T$-tractability on the restricted domain $\Omega$ via \eqref{eq:rest_tract_def}, and verifies the sufficiency of \eqref{eq:rest_tractiff}.

>>>>

For the case $\theUB(d)> 0$, we utilize the upper bound \eqref{eq:compUP_rest}, specializing to the case of $\thed=d$ and $N = \min\left\{\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right\}$:
\begin{align*}
       \comp(\varepsilon,d)
       & \le T(\varepsilon^{-1},d, \vp) \Biggl [ \frac{\min\left\{\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right\}}{T(\varepsilon^{-1},d, \vp)}  + \underbrace{\sum_{i = \min\left\{\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right\}}^{\theUB(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} + 1/ T(\lambda_{\theUB(d), d}^{-1},d,\vp) \text{ by \eqref{eq:strong_rest_tractiff}} }
        \Biggr] \\
       & \le T(\varepsilon^{-1},d,\vp)\left[\frac{ L_{\vp}\, T(0,d,\vp)+1}{T(0,d, \vp)} + S_{\vp} + \frac{1}{T(\lambda_{\theUB(d), d}^{-1},d,\vp)} \right]
       \qquad \text{by \eqref{eq:Tnondecreasing}}\\
       & \le T(\varepsilon^{-1},d,\vp) \underbrace{\left[L_{\vp} + \frac{2}{T(0,1, \vp)} + S_{\vp} \right]}_{=:C_{\vp}}
       \qquad \text{by \eqref{eq:Tnondecreasing}}\\
       & =  C_{\vp}T(\varepsilon^{-1},d,\vp).
\end{align*}
This means that we have strong $T$-tractability on the restricted domain $\Omega$ via \eqref{eq:rest_tract_def}, and verifies the sufficiency of \eqref{eq:rest_tractiff}.
